Automated Verification Applied to Stand-alone Solar Photovoltaic Systems: Optimal Sizing and Project Validation

### 2019-07-09 Tex/Old text/chapters/chapter02.tex
thesis updated text

It is very important to note that formal verification does not avoid the need for testing~\cite{Bowen95}. Formal verification cannot fix bad assumptions in the design, but it can help identify errors in reasoning which would otherwise be left unverified. In several cases, engineers have reported finding flaws in systems once they reviewed their designs formally~\cite{Kling95}.

>>>>

Worth to mention that formal verification does not avoid the need for testing~\cite{Bowen95}. Formal verification can not fix bad assumptions in the design, but it can help identify errors in reasoning which would otherwise be left unverified. In several cases, engineers have reported finding flaws in systems once they reviewed their designs formally~\cite{Kling95}.

### 2019-07-09 Tex/Old text/chapters/introduction.tex
thesis updated text

The increase in a number of PV systems installed all over the world brings the need for proper modeling and simulation tools for researcher and practitioners involved in their application.

@@

Related to \textbf{automated synthesis} method and the optimal sizing of stand-alone PV systems, this Thesis presents the development of a variant of counterexample guided inductive synthesis (CEGIS) that uses commercial equipment data to deliver commercial list of items. 
Given a correctness specification $\sigma$, our method uses that as starting point 
and then iteratively produces a sequence of candidate solutions that satisfy $\sigma$, 
related to power reliability. In particular, in each iteration, we synthesize sizing of 
stand-alone PV systems but that may not achieve the lowest cost. The candidate solution 
is then verified via symbolic model checking with a lower bound that serves as the minimum 
cost of reference; if the verification step does not fail, the lower bound is adjusted. 
If it fails then a counterexample is provided with an optimal sizing that meets 
power reliability and system cost. Note that in this study, the focus is not on a novel criteria or even optimization objectives. Instead, the novelty relies on an effective approach on the pursuit of the optimal solution of PV systems using formal methods, which outperforms existing state-of-the-art simulation tool.

@@

And linked to \textbf{automated synthesis}, this work makes three major contributions. 
\textbf{First}, the use of automated symbolic verification methods in electrical systems was uncommon in recent prior studies~\cite{abs-1811-09438}, and specifically their use in synthesizing optimal PV sizing is unprecedented. Here, a list of PV components (i.e., PV panels, charge controllers, inverters, and batteries) can be fed to the proposed synthesis method together with user requirements and environment constraints, and our synthesis algorithm based on symbolic model checking can find the optimal solution in technical and economical terms. 
\textbf{Second}, we evaluate different state-of-art symbolic software verifiers with the goal of obtaining the best performance in our verification back-end for synthesizing optimal PV systems, being the first work that performs this type of comparative. 
\textbf{Third}, the experimental results show that our synthesis method is an effective and efficient approach on the pursuit of the optimal solution of PV systems using formal methods, which outperforms existing state-of-the-art simulation tool. As a result, this Thesis marks the first application of a sound and automated formal synthesis approach able to provide accurate results of optimal sizing of stand-alone PV systems. Thus, there is considerably advance the state-of-the-art in applied energy over the last two decades with the goal of optimally designing PV systems.

>>>>

The increase in a number of PV systems installed all over the world brings the need for proper modeling of those equipment and simulation tools for researcher and practitioners involved in their application.

@@

Related to \textbf{automated synthesis} method and the optimal sizing of stand-alone PV systems, this Thesis presents the development of a variant of counterexample guided inductive synthesis (CEGIS) that uses commercial equipment data, user requirements and weather conditions as input. 
Given a correctness specification $\sigma$, the proposed method uses that as starting point 
and then iteratively produces a sequence of candidate solutions that satisfy $\sigma$, 
related to power reliability. In particular, in each iteration, we synthesize sizing of 
stand-alone PV systems but that may not achieve the lowest cost. The candidate solution 
is then verified via symbolic model checking with a lower bound that serves as the minimum 
cost of reference; if the verification step does not fail, the lower bound is adjusted. 
If it fails then a counterexample is provided with an optimal sizing that meets 
power reliability and system cost. Note that in this study, the focus is not on a novel criteria or even optimization objectives. Instead, the novelty relies on an effective approach on the pursuit of the optimal solution of PV systems using formal methods, which outperforms existing state-of-the-art simulation tool.

@@

And linked to \textbf{automated synthesis}, this work makes three major contributions. 
\textbf{First}, the use of automated symbolic verification methods in electrical systems was uncommon in recent prior studies~\cite{abs-1811-09438}, and specifically their use in synthesizing optimal PV sizing is unprecedented. Here, a list of PV components (i.e., PV panels, charge controllers, inverters, and batteries) can be fed to the proposed synthesis method together with user requirements and environment constraints, and the proposed synthesis algorithm based on symbolic model checking can find the optimal solution in technical and economical terms. 
\textbf{Second}, we evaluate different state-of-art symbolic software verifiers with the goal of obtaining the best performance in the verification back-end for synthesizing optimal PV systems, being the first work that performs this type of comparative. 
\textbf{Third}, the experimental results show that the proposed synthesis method is an effective and efficient approach on the pursuit of the optimal solution of PV systems using formal methods, which outperforms existing state-of-the-art simulation tool. As a result, this Thesis marks the first application of a sound and automated formal synthesis approach able to provide accurate results of optimal sizing of stand-alone PV systems. Thus, there is considerably advance the state-of-the-art in applied energy over the last two decades with the goal of optimally designing PV systems.
